Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface

### 2022-07-20 main.tex
:pencil: Summarize input distribution design

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{array}
\usepackage{bookmark}
\usepackage{circuitikz}
\usepackage{cite}
\usepackage{colortbl}
\usepackage{environ}
\usepackage{fixmath}
\usepackage{grffile}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{multirow}
\usepackage{pgffor}
\usepackage{pgfgantt}
\usepackage{pgfplots}
\usepackage{physics}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage{tcolorbox}
\usepackage{tikz}
\usepackage{url}
\usepackage{xcolor}
\usepackage[T1]{fontenc}
\usepackage[acronym]{glossaries-extra}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage[short]{optidef}
\usepackage[subtle]{savetrees}

@@

\makeatletter
\tikzset{
	block/.style={draw,rectangle,align=center},
    from/.style args={#1 to #2}{
        above right={0cm of #1},
        /utils/exec=\pgfpointdiff
            {\tikz@scan@one@point\pgfutil@firstofone(#1)\relax}
            {\tikz@scan@one@point\pgfutil@firstofone(#2)\relax},
        minimum width/.expanded=\the\pgf@x,
        minimum height/.expanded=\the\pgf@y
	}
}
\makeatother

@@

@@

	\begin{subsection}{SR: Backscatter Modulation}
		% Backscatter sources encode self message by \emph{randomly changing reflection states.} For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding complex constellation point $c_m$ by \cite{Thomas2012a}
		Backscatter sources encode self message by \emph{random reflection states variation.} For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{complex constellation point $c_m$} by \cite{Thomas2012a}
		\begin{equation}
			\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
			\label{eq:backscatter_modulation}
		\end{equation}
		where $\alpha \in [0,1]$ is the amplitude reflect ratio that controls the harvest-scatter tradeoff at the direction of interest.
		% When the \gls{csi} and reflection alphabet $\{\Gamma_1,\ldots,\Gamma_M\}$ are available at the reader, it can decode the tag message from the observed scattered signal.
		% ! Use larger alpha in simulation: for high-order QAM, some constellation point may harvests more power than others

@@

	\begin{subsection}{IRS: Channel Reconfiguration}
		% \gls{irs} elements assist legacy transmission by \emph{deterministically choosing phase shifts} based on relevant \gls{csi}. For a reflecting element with $M$ candidate states, reflection coefficient $\Gamma_m$ maps to the corresponding phase shift $\theta_m$ by \cite{Wu2018}
		\gls{irs} elements assist legacy transmission by \emph{deterministic phase shifts selection} based on relevant \gls{csi}.
		For a reflecting element with $M$ candidate states, reflection coefficient $\Gamma_m$ relates to the corresponding \emph{phase shift $\theta_m$} by \cite{Wu2018}
		\begin{equation}
			\Gamma_m = \beta_m \exp(j \theta_m),
		\end{equation}
		where $\beta_m \in [0,1]$ is overall amplitude reflect ratio of state $m$.
		% Based on relevant \gls{csi}
	\end{subsection}
	% Tags periodically switch between different states to perform backscatter modulation.
	% For $M$-ary \gls{qam}, the complex constellation point $c_m \in \mathcal{C}$ maps to the reflection coefficient by \cite{Thomas2012a}
	% \begin{equation}
	% 	\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
	% 	\label{eq:backscatter_modulation}
	% \end{equation}
	% where $\alpha \in [0,1]$ models the harvest-backscatter ratio at the direction of interest.
	% For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.

@@

		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, and the node $k$-user backward channel as $h_{\mathrm{B},k}$. Also, define the cascaded channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, and $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$.
		% Let $x_{\mathcal{K}} \triangleq \{x_k : k \in \mathcal{K}\}$ be the backscatter symbols of all Metascatters.
		Let $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all Metascatters.
		Consider the signal model during one backscatter block (i.e., $N$ primary blocks).
		% We assume the primary symbol follows standard \gls{cscg} distribution and the backscatter symbol of all tags employs $M$-\gls{qam}.
		Under perfect synchronization, the equivalent primary channel is a function of backscatter symbols
		\begin{subequations}
			\label{eq:equivalent_channel}
			\begin{align}
				\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}})
				 & \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k \\
				 & = \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}},
			\end{align}
		\end{subequations}
		where $\alpha_k$ is the amplitude reflect ratio of Metascatter $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{R}_+^{K \times 1}$, $x_k \in \mathcal{X} \triangleq \{\Gamma_1,\ldots,\Gamma_M\}$ is the backscatter symbol of Metascatter $k$, and $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathbb{C}^{K \times 1}$. The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
		\begin{equation}
			y[n] = \boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \boldsymbol{w} s[n] + v[n],
		\end{equation}
		where $s \sim \mathcal{CN}(0,1)$ is the primary symbol, $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn}, and $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active beamforming vector with average power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$.
		% The equivalent channel for primary link is subject to backscatter uncertainty
		% The equivalent primary channel is a function of backscatter symbols  as
		% \begin{equation}
		% 	% \boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k.
		% 	\boldsymbol{h}_{\mathrm{E}}^H(\boldsymbol{x}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}}.
		% 	\label{eq:equivalent_channel}
		% \end{equation}

		% where $\alpha_k$ and $x_k$ denote respectively the harvest-backscatter efficiency and backscatter symbol of tag $k$, $s[n]$ and $w[n] \sim \mathcal{CN}(0,\sigma_w^2)$ denote respectively the primary symbol and \gls{awgn} at block $n$, and $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the transmit precoder satisfying power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$.
		% For the ease of notation, we define $x_{\mathcal{K}} \triangleq \{x_k : k \in \mathcal{K}\}$ as the tag input combination, and $\boldsymbol{y} \triangleq \left[y[1],\ldots,y[N]\right]^T \in \mathbb{C}^{N \times 1}$ as the received signal per backscatter symbol period.
		% For primary transmission, the equivalent channel is subject to backscatter modulation uncertainty as
		% \begin{equation}
		% 	\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k.
		% 	\label{eq:equivalent_channel}
		% \end{equation}

@@

			f(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{z^{N-1} e^{-z/\sigma_{m_{\mathcal{K}}}^2}}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!},

@@

		\begin{remark}
			% For a general input distribution, not only the optimal decision thresholds
			The rate-optimal thresholding channel design remains under-investigated, and some attempts were made for single source with binary inputs in \cite{Qian2019b,Nguyen2021b}.
			% The question was only answered for single source with binary inputs in \cite{Qian2019b,Nguyen2021b}.
			% Some attempts for single source with binary inputs were presented in \cite{Qian2019b,Nguyen2021b}.
			For non-binary inputs with general distribution, the optimal decision region for each letter can be non-convex (i.e., with non-adjacent partitions) and the optimal number of thresholds is still unknown.
			% Next, we will restrict the design over convex decision regions.
			Next, we will constrain all decision regions to convex and consider suboptimal threshold design accordingly.
			% For a general input distribution, not only the rate-optimal decision thresholds
			% % Interestingly, the optimal threshold design to maximize the mutual information for a general \gls{dmtc} with a fixed number of output letters remains an open issue.
			% % The reason is that each decision region may contain more than one disjoint partitions (i.e., non-convex) and the number of thresholds are unknown.
			% % Fortunately, for the proposed energy detection, we proved that the \gls{dmtc} capacity can be achieved using only convex decision regions.
			% not only the capacity-achieving thresholding design remains an open problem, but also the optimal number of thresholds for general non-binary-input channels remains unknown.
		\end{remark}
	\end{subsection}

	\begin{subsection}{Achievable Rates}
		Denote the input probability of state $m_k$ of Metascatter node $k$ as $P_k(x_{m_k})$, and define the input probability distribution vector of node $k$ as $\boldsymbol{p}_k \triangleq [P_k(\Gamma_1),\ldots,P_k(\Gamma_M)]^T \in \mathbb{R}^{M \times 1}$. With independent encoding at all nodes, the probability of backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k})$.
		% Denote the input probability distribution vector of tag $k$ as $\boldsymbol{p}_k \triangleq [P_k(x_1),\ldots,P_k(x_M)]^T \in \mathbb{R}^{M \times 1}$, where $P_k(x_{m_k})$ is the probability at state $m_k$.
		% Consider independent encoding at all tags such that the probability of input combination $x_{m_{\mathcal{K}}}$ is $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k})$.
		% The backscatter information function of input combination $x_{m_{\mathcal{K}}}$ is defined as
		Similar to \cite{Rezaeian2004}, we define the backscatter information function between input symbol tuple instance $x_{m_{\mathcal{K}}}$ and output symbol tuple $\hat{x}_{\mathcal{K}}$ as
		\begin{equation}
			I^{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{P(\hat{x}_{m_{\mathcal{K}}'})},
			\label{eq:backscatter_information_function}
		\end{equation}
		where $P(\hat{x}_{m_{\mathcal{K}}'}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$.
		We also define the backscatter marginal information of letter $x_{m_k}$ of node $k$ as
		% Besides, the backscatter marginal information function associated with letter $x_{m_k}$ of tag $k$ is
		\begin{equation}
			% I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
			I^{\mathrm{B}}_{k}(x_{m_k};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I^{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
			\label{eq:backscatter_marginal_information_function}
		\end{equation}
		where $P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) = \prod_{q \in \mathcal{K} \setminus \{k\}} P_{q}(x_{m_{q}})$.
		Moreover, we can write the backscatter mutual information as
		\begin{equation}
			% I^{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{P(\hat{x}_{m_{\mathcal{K}}'})}.
			I^{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I^{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}).
			\label{eq:backscatter_mutual_information}
		\end{equation}

>>>>

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{algorithmicx}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{array}
\usepackage{bookmark}
\usepackage{circuitikz}
\usepackage{cite}
\usepackage{colortbl}
\usepackage{environ}
\usepackage{fixmath}
\usepackage{grffile}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{multirow}
\usepackage{pgffor}
\usepackage{pgfgantt}
\usepackage{pgfplots}
\usepackage{physics}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage{tcolorbox}
\usepackage{tikz}
\usepackage{url}
\usepackage{xcolor}
\usepackage[T1]{fontenc}
\usepackage[acronym]{glossaries-extra}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage[short]{optidef}
\usepackage[subtle]{savetrees}

@@

\makeatletter
\renewcommand{\fnum@algorithm}{\fname@algorithm{} \thealgorithm:}
\tikzset{
	block/.style={draw,rectangle,align=center},
    from/.style args={#1 to #2}{
        above right={0cm of #1},
        /utils/exec=\pgfpointdiff
            {\tikz@scan@one@point\pgfutil@firstofone(#1)\relax}
            {\tikz@scan@one@point\pgfutil@firstofone(#2)\relax},
        minimum width/.expanded=\the\pgf@x,
        minimum height/.expanded=\the\pgf@y
	}
}
\makeatother

@@

% \floatname{algorithm}{Procedure}
\algrenewcommand{\algorithmicrequire}{\textbf{Input:}}
\algrenewcommand{\algorithmicensure}{\textbf{Output:}}

@@

	\begin{subsection}{SR: Backscatter Modulation}
		% Backscatter sources encode self message by \emph{randomly changing reflection states.} For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding complex constellation point $c_m$ by \cite{Thomas2012a}
		Backscatter sources encode self message by \emph{random reflection states variation.} For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{complex constellation point $c_m$} by \cite{Thomas2012a}
		\begin{equation}
			\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
			\label{eq:backscatter_modulation}
		\end{equation}
		where $0 \le \alpha \le 1$ is the amplitude reflect ratio that controls the harvest-scatter tradeoff at the direction of interest.
		% When the \gls{csi} and reflection alphabet $\{\Gamma_1,\ldots,\Gamma_M\}$ are available at the reader, it can decode the tag message from the observed scattered signal.
		% ! Use larger alpha in simulation: for high-order QAM, some constellation point may harvests more power than others

@@

	\begin{subsection}{IRS: Channel Reconfiguration}
		% \gls{irs} elements assist legacy transmission by \emph{deterministically choosing phase shifts} based on relevant \gls{csi}. For a reflecting element with $M$ candidate states, reflection coefficient $\Gamma_m$ maps to the corresponding phase shift $\theta_m$ by \cite{Wu2018}
		\gls{irs} elements assist legacy transmission by \emph{deterministic phase shifts selection} based on relevant \gls{csi}.
		For a reflecting element with $M$ candidate states, reflection coefficient $\Gamma_m$ relates to the corresponding \emph{phase shift $\theta_m$} by \cite{Wu2018}
		\begin{equation}
			\Gamma_m = \beta_m \exp(j \theta_m),
		\end{equation}
		where $0 \le \beta_m \le 1$ is overall amplitude reflect ratio of state $m$.
		% Based on relevant \gls{csi}
	\end{subsection}
	% Tags periodically switch between different states to perform backscatter modulation.
	% For $M$-ary \gls{qam}, the complex constellation point $c_m \in \mathcal{C}$ maps to the reflection coefficient by \cite{Thomas2012a}
	% \begin{equation}
	% 	\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
	% 	\label{eq:backscatter_modulation}
	% \end{equation}
	% where $\alpha \in [0,1]$ models the harvest-backscatter ratio at the direction of interest.
	% For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.

@@

		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, and the node $k$-user backward channel as $h_{\mathrm{B},k}$. Also, define the cascaded channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, and $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$.
		% Let $x_{\mathcal{K}} \triangleq \{x_k : k \in \mathcal{K}\}$ be the backscatter symbols of all Metascatters.
		Let $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all Metascatters.
		Consider the signal model during one backscatter block (i.e., $N$ primary blocks).
		% We assume the primary symbol follows standard \gls{cscg} distribution and the backscatter symbol of all tags employs $M$-\gls{qam}.
		Under perfect synchronization, the equivalent primary channel is a function of backscatter symbols
		\begin{subequations}
			\label{eq:equivalent_channel}
			\begin{align}
				\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}})
				 & \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k   \\
				 & = \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}},
			\end{align}
		\end{subequations}
		where $\alpha_k$ is the amplitude reflect ratio of Metascatter $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{R}_+^{K \times 1}$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ is the backscatter symbol of Metascatter $k$, and $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathbb{C}^{K \times 1}$. The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
		\begin{equation}
			y[n] = \boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \boldsymbol{w} s[n] + v[n],
		\end{equation}
		where $s \sim \mathcal{CN}(0,1)$ is the primary symbol, $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn}, and $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active beamforming vector with average power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$.
		% The equivalent channel for primary link is subject to backscatter uncertainty
		% The equivalent primary channel is a function of backscatter symbols  as
		% \begin{equation}
		% 	% \boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k.
		% 	\boldsymbol{h}_{\mathrm{E}}^H(\boldsymbol{x}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}}.
		% 	\label{eq:equivalent_channel}
		% \end{equation}

		% where $\alpha_k$ and $x_k$ denote respectively the harvest-backscatter efficiency and backscatter symbol of tag $k$, $s[n]$ and $w[n] \sim \mathcal{CN}(0,\sigma_v^2)$ denote respectively the primary symbol and \gls{awgn} at block $n$, and $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the transmit precoder satisfying power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$.
		% For the ease of notation, we define $x_{\mathcal{K}} \triangleq \{x_k : k \in \mathcal{K}\}$ as the tag input combination, and $\boldsymbol{y} \triangleq \left[y[1],\ldots,y[N]\right]^T \in \mathbb{C}^{N \times 1}$ as the received signal per backscatter symbol period.
		% For primary transmission, the equivalent channel is subject to backscatter modulation uncertainty as
		% \begin{equation}
		% 	\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k.
		% 	\label{eq:equivalent_channel}
		% \end{equation}

@@

			f(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{z^{N-1} \exp(-z/\sigma_{m_{\mathcal{K}}}^2)}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!},
			% f(z|\mathcal{H}_{m_{\mathcal{K}}}) = \frac{z^{N-1} \exp(\frac{-z}{\sigma_{m_{\mathcal{K}}}^2})}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!},

@@

		\begin{remark}
			% For a general input distribution, not only the optimal decision thresholds
			The rate-optimal thresholding channel design remains under-investigated, and some attempts were made for single source with binary inputs in \cite{Qian2019b,Nguyen2021b}.
			% The question was only answered for single source with binary inputs in \cite{Qian2019b,Nguyen2021b}.
			% Some attempts for single source with binary inputs were presented in \cite{Qian2019b,Nguyen2021b}.
			For non-binary inputs with general distribution, the optimal decision region for each letter can be non-convex (i.e., with non-adjacent partitions) and the optimal number of thresholds is still unknown.
			% Next, we will restrict the design over convex decision regions.
			% For a general input distribution, not only the rate-optimal decision thresholds
			% % Interestingly, the optimal threshold design to maximize the mutual information for a general \gls{dmtc} with a fixed number of output letters remains an open issue.
			% % The reason is that each decision region may contain more than one disjoint partitions (i.e., non-convex) and the number of thresholds are unknown.
			% % Fortunately, for the proposed energy detection, we proved that the \gls{dmtc} capacity can be achieved using only convex decision regions.
			% not only the capacity-achieving thresholding design remains an open problem, but also the optimal number of thresholds for general non-binary-input channels remains unknown.
		\end{remark}
		In the following context, we restrict all decision regions to convex and optimize decision thresholds accordingly. That is, for any bijective mapping $f : m_{\mathcal{K}} \to \mathcal{L} \triangleq \{1,\ldots,M^K\}$, the decision region of letter $l \in \mathcal{L}$ is defined as $\mathcal{R}_l \triangleq [t_{l-1},t_l)$, where $t_{l-1}<t_l$. We also define the decision threshold vector as $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^T \in \mathbb{R}_+^{(L+1) \times 1}$.
	\end{subsection}

	\begin{subsection}{Achievable Rates}
		Denote the input probability of state $m_k$ of Metascatter node $k$ as $P_k(x_{m_k})$, and define the input probability distribution vector of node $k$ as $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^T \in \mathbb{R}^{M \times 1}$. With independent encoding at all nodes, the probability of backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k})$.
		% Denote the input probability distribution vector of tag $k$ as $\boldsymbol{p}_k \triangleq [P_k(x_1),\ldots,P_k(x_M)]^T \in \mathbb{R}^{M \times 1}$, where $P_k(x_{m_k})$ is the probability at state $m_k$.
		% Consider independent encoding at all tags such that the probability of input combination $x_{m_{\mathcal{K}}}$ is $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k})$.
		% The backscatter information function of input combination $x_{m_{\mathcal{K}}}$ is defined as
		Similar to \cite{Rezaeian2004}, we define the backscatter information function between input symbol tuple instance $x_{m_{\mathcal{K}}}$ and output symbol tuple $\hat{x}_{\mathcal{K}}$ as
		\begin{equation}
			I^{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{P(\hat{x}_{m_{\mathcal{K}}'})},
			\label{eq:backscatter_information_function}
		\end{equation}
		where $P(\hat{x}_{m_{\mathcal{K}}'}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$.
		We also define the backscatter marginal information of letter $x_{m_k}$ of node $k$ as
		% Besides, the backscatter marginal information function associated with letter $x_{m_k}$ of tag $k$ is
		\begin{equation}
			% I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
			I^{\mathrm{B}}_{k}(x_{m_k};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I^{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
			\label{eq:backscatter_marginal_information}
		\end{equation}
		where $P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) = \prod_{q \in \mathcal{K} \setminus \{k\}} P_{q}(x_{m_{q}})$.
		Moreover, we can write the backscatter mutual information as
		\begin{equation}
			% I^{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{P(\hat{x}_{m_{\mathcal{K}}'})}.
			I^{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I^{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}).
			\label{eq:backscatter_mutual_information}
		\end{equation}

		% Once the tag input combination is successfully decoded, the backscatter uncertainty can be eliminated and the equivalent channel for primary transmission can be updated by \eqref{eq:equivalent_channel}.
		Once backscatter symbols are successfully decoded, we can eliminate modulation uncertainty and retrieve equivalent primary channel by \eqref{eq:equivalent_channel}. We define the primary information function conditioned on backscatter symbol tuple $x_{m_{\mathcal{K}}}$ as
		% \begin{equation}
		% 	I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) \triangleq \log \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\right),
		% 	\label{eq:primary_information_function}
		% \end{equation}
		\begin{equation}
			I^{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
			\label{eq:primary_information_function}
		\end{equation}
		the primary marginal information conditioned on letter $x_{m_k}$ of node $k$ as
		% the primary marginal information function associated with letter $x_{m_k}$ of tag $k$ is
		\begin{equation}
			I^{\mathrm{P}}_{k}(s;y|x_{m_k}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I^{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}),
			\label{eq:primary_marginal_information}
		\end{equation}
		and the primary ergodic mutual information as
		% and the primary (ergodic) mutual information is
		\begin{equation}
			% I^{\mathrm{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \log \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\right).
			I^{\mathrm{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I^{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}).
			\label{eq:primary_mutual_information}
		\end{equation}
